Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-12 research_class/paper.tex
Add preferred comma.

However, requiring application messages and application state to
traverse the back-end servers is not always desirable for various
reasons including the following:

>>>>

However, requiring application messages and application state to
traverse the back-end servers is not always desirable for various
reasons, including the following:
